### 2025-07-09 paper/sections/experiments.qmd
all done here

>>>>

<!-- Final Results -->
<!---->
<!-- Columns 1-3 show mean outcome +- TWO (2) bootstrapped standard errors. -->
<!---->
<!-- - IP: significant and in many cases substantial reduction in implausibility, except for OL and Adult (both insfignficant) -->
<!-- - IP*: significant and in many cases substantial reduction (up to 90%) in implausibility, except for MNIST and OL. -->
<!-- - Cost: significant and in some cases substantial reduction, except for Adult, MNIST (both insignificant) and Credit (significant increase in costs). -->
